---
title: "Research Compendium practice"
author:
  - Chih-Fu Yeh:  
      email: yehcf@stanford.edu
      institute: Stanford University
      correspondence: true
      
  
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/nature.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 

--- 

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

<!-- The actual document text starts here: -->

# Introduction

This is a replication of figure 2A from @hirt2017 (Fig. \@ref(fig:fig2a))

# Background

# Methods

# Results

```{r load}

library(maxspeed)
library(dplyr)
library(ggplot2)
maxspeed <- readRDS("../data/derived_data/maxspeed.RDS")
```

```{r fig2a, fig.cap="Replication of figure 2a from [@hirt2017]"}
palette <- list(green = "#83CE3D",
                orange = "#E39F2F",
                blue = "#5F9FA1")

fly_dat <- filter(maxspeed, locomotion == "flying")
fly_model <- fit_maxspeed(fly_dat)
fly_spd <- tibble(
  mass_kg = seq(min(fly_dat$mass_kg), max(fly_dat$mass_kg), length.out = 1000),
  max_spd_kmh = predict_maxspeed(mass_kg, fly_model)
)

run_dat <- filter(maxspeed, locomotion == "running")
run_model <- fit_maxspeed(run_dat)
run_spd <- tibble(
  mass_kg = seq(min(run_dat$mass_kg), max(run_dat$mass_kg), length.out = 1000),
  max_spd_kmh = predict_maxspeed(mass_kg, run_model)
)

swm_dat <- filter(maxspeed, locomotion == "swimming")
swm_model <- fit_maxspeed(swm_dat)
swm_spd <- tibble(
  mass_kg = seq(min(swm_dat$mass_kg), max(swm_dat$mass_kg), length.out = 1000),
  max_spd_kmh = predict_maxspeed(mass_kg, swm_model)
)

ggplot(fly_dat, aes(x = mass_kg, y = max_spd_kmh)) +
  geom_point(color = palette$green, size = 0.5, shape = 15) +
  geom_point(data = run_dat, color = palette$orange, size = 0.5, shape = 16) +
  geom_point(data = swm_dat, color = palette$blue, size = 0.5, shape = 17) +
  geom_line(data = fly_spd, 
            color = palette$green, 
            size = 1.25) +
  geom_line(data = fly_spd, 
            color = "white", 
            size = 0.5) +
  geom_line(data = run_spd, 
            color = palette$orange, 
            size = 1.25) +
  geom_line(data = run_spd, 
            color = "white", 
            size = 0.5) +
  geom_line(data = swm_spd, 
            color = palette$blue, 
            size = 1.25) +
  geom_line(data = swm_spd, 
            color = "white", 
            size = 0.5) +
  scale_x_log10("Body mass (kg)",
                limits = 10^c(-10, 7),
                breaks = 10^c(-10, -6, -2, 1, 4, 7),
                labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  scale_y_log10(bquote(Speed~(km~h^-1)),
                limits = 10^c(-2, 3),
                breaks = 10^(-2:3),
                labels = c("0.01", "0.1", "1", "10", "100", "1,000")) +
  annotation_logticks() +
  theme_classic() +
  theme(aspect.ratio = 1)
```

<!-- Here's some example analysis code: -->

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
